Measuring Perceptions and Preferences for Meritocracy

### 2020-07-26 docs/paper.tex
update paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Perceptions and Preferences for Meritocracy},
  colorlinks=true,
  linkcolor=blue,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\title{Perceptions and Preferences for Meritocracy}
\date{}

@@

Based on the previous limitations in the measurement of meritocracy
presented in the previous section, in this paper we propose and test an
instrument with the following characteristics:

\begin{itemize}
\tightlist
\item
  Multidimensional, incorporating previous distinctions between
  preferences and perceptions as well as between meritocratic and
  non-meritocratic aspects.
\item
  Multiple indicators for each dimension, in order to account for
  measurement error in a confirmatory factor analysis context.
\item
  Based on previous indicators as far as possible, for the sake of
  comparability between studies
\item
  Brief, as to be used in a regular survey. In this point it differs for
  instance from the proposal of the ``Preference for the Merit Principle
  Scale'' (Davey et al.
  \protect\hyperlink{ref-davey_preference_1999}{1999}), as they use 15
  items just for one dimension (besides the problem of reverse-coding
  non-meritocratic items).
\end{itemize}

. . .

The proposed measurement framework is based on two axis of analysis, as
depicted in Table 1:

Table 1: Dimensions of meritocratic beliefs.

\begin{longtable}[]{@{}lll@{}}
\toprule
& Perceptions & Preferences\tabularnewline
\midrule
\endhead
\emph{Meritocracy} & &\tabularnewline
\emph{Non-meritocracy} & &\tabularnewline
\bottomrule
\end{longtable}

The first axis distinguishes between different types of ``beliefs'',
using instead the terms perceptions and preferences for meritocracy
(Duru-Bellat and Tenret
\protect\hyperlink{ref-duru-bellat_whos_2012}{2012}\protect\hyperlink{ref-duru-bellat_whos_2012}{b};
Son Hing et al. \protect\hyperlink{ref-son_hing_merit_2011-1}{2011}).
Perceptions refers to the extent to which people see meritocracy working
in their society, which in terms of measurement relates to the ``reasons
to get ahead'' battery, whereas preferences refer to normative
expectations that are usually linked to a ``should'' expression
(e.g.~whether hard work should be related to payment). The second axis
consider the distinction between meritocratic and non-meritocratic
dimensions (Reynolds and Xian
\protect\hyperlink{ref-reynolds_perceptions_2014}{2014}\protect\hyperlink{ref-reynolds_perceptions_2014}{b}).
This aspect has been usually treated as different ends of a same
continuum in part of the previous research, an assumption that requieres
empirical scrutiny. These non-meritocratic elements usually refer to the
use of personal contacts or family advantages to get ahead in life.

Regarding the selection of indicators, most of them some adaptations of
previous items that where streamlined in order to a better fit with the
specific dimensions. For meritocratic indicators we use effort and
talent as the main components of the traditional concept of merit as
defined by Young (\protect\hyperlink{ref-young_rise_1962}{1962}),
whereas for non-meritocratic dimensions we use having rich parents and
good contacts. The description of the specific items is presented in the
methodology section.

\textbf{Hypotheses}

\begin{itemize}
\item
  H1. The perception of meritocracy is a latent variable based on
  indicators of the importance attributed to talent and the effort to
  get ahead in life.
\item
  H2. The non-meritocratic perception is a latent variable that derives
  from two indicators related to the agreement with the statement that
  people with contacts and rich parents manage to get ahead.
\item
  H3. Meritocratic preferences behave as the latent variable based on a
  normative value of effort and talent.
\item
  H4. Non-meritocratic preferences behave as a latent variable based on
  the normative value of the use of personal contacts and having rich
  parents.
\end{itemize}

@@

The data was obtained through an online questionnaire which was part of
a larger study on meritocracy and preferences developed in Chile in 2019
and funded by the national scientific agency FONDECYT. The questionnaire
was programmed in Qualtrics and the fieldwork was in charge of an
external online survey agency
(\href{www.netquest.cl}{netquest.cl})during December 2019 and January
2020. The sample was selected from a non-probabilistic design in three
large cities in Chile. The quota method based on age, sex and
educational level was used. Quotas were generated based on the survey of
the Public Studies Center (CEP, 2019), which has a high prestige in the
country and is also the counterpart agency of ISSP (International Social
Survey Programme) in Chile. A total sample of 2141 people was collected,
excluding those who did not answer the questions on the scale and those
who did not accept informed consent. As it usually occurs online
samples, there were some limitations in achieving the quotas for lower
educational levels.

@@

The proposed scale of perceptions and preferences about meritocracy
consists of 8 indicators that are grouped into 4 dimensions referred
above: Perceptions (meritocratic/nonmeritocratic) and preferences
(meritocratic/non-meritocratic). In order to achieve at least some
comparability with previous studies, the questions were adapted from the
items battery ``reasons to get ahead'' (ISSP/GSS), which are mostly used
for operationalizing meritocracy in previous empirical studies (Mijs
\protect\hyperlink{ref-mijs_paradox_2019}{2019}\protect\hyperlink{ref-mijs_paradox_2019}{b};
Duru-Bellat and Tenret
\protect\hyperlink{ref-duru-bellat_whos_2012}{2012}\protect\hyperlink{ref-duru-bellat_whos_2012}{b};
Reynolds and Xian
\protect\hyperlink{ref-reynolds_perceptions_2014}{2014}\protect\hyperlink{ref-reynolds_perceptions_2014}{b}).
The eight items ordered according to dimensions are presented in Table
2. These 8 likert-type items have 5 response alternatives ranging from
``Completely disagree''(1) to ``Completely agree'' (5).

Table 2: Items according to dimension.

\includegraphics{../input/images/tabla2.png}

@@

With the objective of evaluating the effect of the order of the
indicators, the respondents (\emph{n = 2141}) were randomly divided into
three groups as explained in \textbf{Diagram 1}. The scale was presented
to the first group (\emph{n = 712}) in the order that appears in Table
2, in such a way that the items of the same factor are found together.
The second group (\emph{n = 717})was presented with the scale with the
items of the same factor separated from each other, in such a way that
they were consulted at the same time for their perceptions and
preferences of a particular topic (e.g.~distribution according to
effort). Finally, in the third group (\emph{n = 712}) the items were
completely randomized.

Diagram 1: Survey flow

\includegraphics{../input/images/app_mod.png}

@@

\hypertarget{conclusiones}{%
\section{Conclusiones}\label{conclusiones}}

@@

\leavevmode\hypertarget{ref-Bay-ChengTrackingHomoOeconomicus2015}{}%
Bay-Cheng, Laina Y., Caroline C. Fitz, Natalie M. Alizaga, and Alyssa N.
Zucker. 2015. ``Tracking Homo Oeconomicus: Development of the Neoliberal
Beliefs Inventory.'' \emph{Journal of Social and Political Psychology} 3
(1): 71--88. \url{https://doi.org/10.5964/jspp.v3i1.366}.

@@

\leavevmode\hypertarget{ref-BubakPerceptionsmeritocracynote2019}{}%
Bubak, Oldrich. 2019. ``Perceptions of Meritocracy: A Note on China.''
\emph{Asian Journal of Comparative Politics} 4 (2): 192--209.
\url{https://doi.org/10.1177/2057891118806065}.

@@

\leavevmode\hypertarget{ref-Duru-BellatWhoMeritocracyIndividual2012b}{}%
Duru-Bellat, Marie, and Elise Tenret. 2012a. ``Who's for Meritocracy?
Individual and Contextual Variations in the Faith.'' \emph{Comparative
Education Review} 56 (2): 223--47. \url{https://doi.org/10.1086/661290}.

\leavevmode\hypertarget{ref-duru-bellat_whos_2012}{}%
---------. 2012b. ``Who's for Meritocracy? Individual and Contextual
Variations in the Faith.'' \emph{Comparative Education Review} 56 (2):
223--47. \url{https://doi.org/10.1086/661290}.

\leavevmode\hypertarget{ref-GenerettStoriesWeTell2020}{}%
Generett, Gretchen Givens, and Amy M. Olson. 2020. ``The Stories We
Tell: How Merit Narratives Undermine Success for Urban Youth.''
\emph{Urban Education} 55 (3): 394--423.
\url{https://doi.org/10.1177/0042085918817342}.

\leavevmode\hypertarget{ref-GirerdNeoliberalismIdeologicalBarrier2020}{}%
Girerd, Lola, and Virginie Bonnot. 2020. ``Neoliberalism: An Ideological
Barrier to Feminist Identification and Collective Action.'' \emph{Social
Justice Research} 33 (1): 81--109.
\url{https://doi.org/10.1007/s11211-020-00347-8}.

@@

\leavevmode\hypertarget{ref-MaitnerEmotionalreactionsunequal2015}{}%
Maitner, Angela T. 2015. ``Emotional Reactions to Unequal Payment: The
Impact of Meritocratic Ideology and Salary Negotiability.'' \emph{Group
Processes \& Intergroup Relations} 18 (2): 153--72.
\url{https://doi.org/10.1177/1368430214542255}.

\leavevmode\hypertarget{ref-MajorPerceiveddiscriminationworldview2007}{}%
Major, Brenda, Cheryl R. Kaiser, Laurie T. O'Brien, and Shannon K.
McCoy. 2007. ``Perceived Discrimination as Worldview Threat or Worldview
Confirmation: Implications for Self-Esteem.'' \emph{Journal of
Personality and Social Psychology} 92 (6): 1068--86.
\url{https://doi.org/10.1037/0022-3514.92.6.1068}.

@@

\leavevmode\hypertarget{ref-Meredithsocietydivisibleblessed2020}{}%
Meredith, Stephen. 2020. ``A `Society \ldots{} Divisible into the
Blessed and the Unblessed': Michael Young and Meritocracy in Postwar
Britain: Michael Young and Meritocracy in Postwar Britain.'' \emph{The
Political Quarterly}, March.
\url{https://doi.org/10.1111/1467-923X.12837}.

\leavevmode\hypertarget{ref-MijsParadoxInequalityIncome2019b}{}%
Mijs, Jonathan J B. 2019a. ``The Paradox of Inequality: Income
Inequality and Belief in Meritocracy Go Hand in Hand.''
\emph{Socio-Economic Review}, January.
\url{https://doi.org/10.1093/ser/mwy051}.

\leavevmode\hypertarget{ref-mijs_paradox_2019}{}%
---------. 2019b. ``The Paradox of Inequality: Income Inequality and
Belief in Meritocracy Go Hand in Hand.'' \emph{Socio-Economic Review},
January. \url{https://doi.org/10.1093/ser/mwy051}.

@@

\leavevmode\hypertarget{ref-OwensENGINESSOCIALMOBILITY2020}{}%
Owens, John, and Tania de St Croix. 2020. ``ENGINES OF SOCIAL MOBILITY?
NAVIGATING MERITOCRATIC EDUCATION DISCOURSE IN AN UNEQUAL SOCIETY.''
\emph{British Journal of Educational Studies}, January, 1--21.
\url{https://doi.org/10.1080/00071005.2019.1708863}.

\leavevmode\hypertarget{ref-PerezAdvancingcareersmerit2020}{}%
Pérez, Andrés, and Ida Sabelis. 2020. ``Advancing Careers Through
`Merit': A Rationalized-Sensemaking Narrative in Hierarchical
Organizations.'' \emph{Culture and Organization} 26 (4): 315--32.
\url{https://doi.org/10.1080/14759551.2019.1601723}.

\leavevmode\hypertarget{ref-PikettyCapitalTwentyFirstCentury2014b}{}%
Piketty, Thomas. 2014. \emph{Capital in the Twenty-First Century}.
Translated by Arthur Goldhammer. Cambridge Massachusetts: The Belknap
Press of Harvard University Press.

\leavevmode\hypertarget{ref-PremingerMeritocracyserviceethnocracy2020}{}%
Preminger, Jonathan. 2020. ``Meritocracy in the Service of Ethnocracy.''
\emph{Citizenship Studies} 24 (2): 247--63.
\url{https://doi.org/10.1080/13621025.2020.1720604}.

\leavevmode\hypertarget{ref-ReayPerilsPenaltiesMeritocracy2020}{}%
Reay, Diane. 2020. ``The Perils and Penalties of Meritocracy:
Sanctioning Inequalities and Legitimating Prejudice.'' \emph{The
Political Quarterly}, March, 1467--923X.12829.
\url{https://doi.org/10.1111/1467-923X.12829}.

\leavevmode\hypertarget{ref-ReynoldsPerceptionsMeritocracyLand2014b}{}%
Reynolds, Jeremy, and He Xian. 2014a. ``Perceptions of Meritocracy in
the Land of Opportunity.'' \emph{Research in Social Stratification and
Mobility} 36 (June): 121--37.
\url{https://doi.org/10.1016/j.rssm.2014.03.001}.

\leavevmode\hypertarget{ref-reynolds_perceptions_2014}{}%
---------. 2014b. ``Perceptions of Meritocracy in the Land of
Opportunity.'' \emph{Research in Social Stratification and Mobility} 36
(June): 121--37. \url{https://doi.org/10.1016/j.rssm.2014.03.001}.

@@

\leavevmode\hypertarget{ref-TrumpWhenwhyeconomic2020}{}%
Trump, Kris-Stella. 2020. ``When and Why Is Economic Inequality Seen as
Fair.'' \emph{Current Opinion in Behavioral Sciences} 34 (August):
46--51. \url{https://doi.org/10.1016/j.cobeha.2019.12.001}.

\leavevmode\hypertarget{ref-WitteveenReconsideringmeritocraticpower2020a}{}%
Witteveen, Dirk, and Paul Attewell. 2020. ``Reconsidering the
`Meritocratic Power of a College Degree'.'' \emph{Research in Social
Stratification and Mobility} 66 (April): 100479.
\url{https://doi.org/10.1016/j.rssm.2020.100479}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Measuring Perceptions and Preferences for Meritocracy},
  colorlinks=true,
  linkcolor=blue,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=0.78in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{caption}
\captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

\title{Measuring Perceptions and Preferences for Meritocracy}
\author{}
\date{\vspace{-2.5em}}

@@

Based on the previous limitations and confussions in the measurement of
meritocracy presented in the previous section, in this paper we propose
and test an instrument with the following characteristics:

\begin{itemize}
\item
  Multidimensional, incorporating previous distinctions between
  preferences and perceptions as well as between meritocratic and
  non-meritocratic aspects.
\item
  Multiple indicators for each dimension, in order to account for
  measurement error in a confirmatory factor analysis context.
\item
  Based on previous indicators as far as possible, for the sake of
  comparability between studies
\item
  Brief, as to be used in a regular survey. In this point it differs for
  instance from the proposal of the ``Preference for the Merit Principle
  Scale'' (Davey et al.
  \protect\hyperlink{ref-davey_preference_1999}{1999}), as they use 15
  items just for one dimension (besides the problem of reverse-coding
  non-meritocratic items).
\end{itemize}

The proposed measurement framework is depicted in Figure 1:

\includegraphics[width=0.6\textwidth,height=\textheight]{../input/images/generalf.png}

The columns Perceptions and Preferences represent the distinction
between this two concepts, usually confused under the label ``beliefs''.
Perceptions refers to the extent to which people see that meritocracy
functions or applies in their society, which in terms of measurement
relates to items such as ``I think hard work is important to get ahead
in society'', whereas preferences refer to normative expectations that
are usually linked to a ``should'' expression (e.g.~whether hard work
should be related to payment). The rows in the table of Figure 1
consider the distinction between meritocratic and non-meritocratic
dimensions (Reynolds and Xian
\protect\hyperlink{ref-reynolds_perceptions_2014}{2014}). This aspect
has been usually treated as different ends of a same continuum in part
of the previous research, an assumption that requieres empirical
scrutiny. These non-meritocratic elements usually refer to the use of
personal contacts or family advantages to get ahead in life.

Regarding the selection of indicators, most of them are taken or adapted
from previous studies for the sake of comparability. For meritocratic
indicators we use effort and talent as the main components of the
traditional concept of merit as defined by Young
(\protect\hyperlink{ref-young_rise_1962}{1962}), whereas for
non-meritocratic dimensions we use having rich parents and good
contacts. The description of the specific items is presented in the
methodology section.

The research hypotheses behind this conceptualization are the following:

\begin{itemize}
\item
  H1. The perception of meritocracy is a latent variable based on
  indicators of the importance attributed to talent and the effort to
  get ahead in life.
\item
  H2. The non-meritocratic perception is a latent variable that derives
  from two indicators related to the agreement with the statement that
  people with contacts and rich parents manage to get ahead.
\item
  H3. Meritocratic preferences are a latent variable based on a
  normative value of effort and talent.
\item
  H4. Non-meritocratic preferences are a latent variable based on the
  normative value of the use of personal contacts and having rich
  parents.
\end{itemize}

@@

The data was obtained through an online questionnaire which was part of
a larger study on meritocracy and preferences developed in Chile in 2019
and funded by the national scientific agency FONDECYT. The questionnaire
was programmed in Qualtrics and the fieldwork was in charge of an
external online survey agency (\href{www.netquest.cl}{netquest.cl})
during December 2019 and January 2020. The sample was selected from a
non-probabilistic design in three large cities in Chile. The quota
method based on age, sex and educational level was used. Quotas were
generated based on the survey of the Public Studies Center (CEP, 2019),
which has a high prestige in the country and is also the counterpart
agency of ISSP (International Social Survey Programme) in Chile. A total
sample of 2,141 people was collected, excluding those who did not answer
the questions on the scale and those who did not accept informed
consent. As it usually occurs online samples, there were some
limitations in achieving the quotas for lower educational levels.

@@

The proposed scale of perceptions and preferences about meritocracy
consists of 8 indicators that are grouped into the 4 dimensions referred
above: Perceptions (meritocratic/non-meritocratic) and preferences
(meritocratic/non-meritocratic). In order to achieve at least some
comparability with previous studies, the questions were adapted from the
items battery ``reasons to get ahead'' (ISSP/GSS), which are mostly used
for operationalizing meritocracy in previous empirical studies (Mijs
\protect\hyperlink{ref-mijs_paradox_2019}{2019}; Duru-Bellat and Tenret
\protect\hyperlink{ref-duru-bellat_whos_2012}{2012}; Reynolds and Xian
\protect\hyperlink{ref-reynolds_perceptions_2014}{2014}). The eight
items ordered according to dimensions are presented in Table 2. These 8
likert-type items have 5 response alternatives ranging from ``Completely
disagree''(1) to ``Completely agree'' (5).

\begin{table}[!h]

\caption{\label{tab:unnamed-chunk-6}Items according to dimension.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{14}{16}\selectfont
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{2 cm}>{\raggedright}X>{\raggedright}X}
\toprule
Dimension & Factor & Statement (english) & Statement (spanish)\\
\midrule
 &  & Those who try harder get greater rewards than those who work less. & Quienes más se esfuerzan logran obtener mayores recompensas que quienes se esfuerzan menos.\\
\cmidrule{3-4}
 & \multirow{-2}{2 cm}{\raggedright\arraybackslash Meritocratic} & Those who have more talent achieve greater rewards than those who have less talent. & Quienes poseen más talento logran obtener mayores recompensas que quienes poseen menos talento.\\
\cmidrule{2-4}
 &  & Those who have rich parents succeed. & Quienes tienen padres ricos logran salir adelante.\\
\cmidrule{3-4}
\multirow{-4}{1.5cm}{\raggedright\arraybackslash Perception} & \multirow{-2}{2 cm}{\raggedright\arraybackslash Non meritocratic} & Those who have good contacts succeed. & Quienes tienen buenos contactos logran salir adelante.\\
\cmidrule{1-4}
 &  & Those who try harder should get greater rewards than those who work less. & Quienes más se esfuerzan deberían obtener mayores recompensas que quienes se esfuerzan menos.\\
\cmidrule{3-4}
 & \multirow{-2}{2 cm}{\raggedright\arraybackslash Meritocratic} & Those who have more talent should get greater rewards than those who have less talent. & Quienes poseen más talento deberían obtener mayores recompensas que quienes poseen menos talento.\\
\cmidrule{2-4}
 &  & It's fine that those with rich parents get ahead. & Está bien que quienes tienen padres ricos salgan adelante.\\
\cmidrule{3-4}
\multirow{-4}{1.5cm}{\raggedright\arraybackslash Preference} & \multirow{-2}{2 cm}{\raggedright\arraybackslash Non meritocratic} & It's fine that those who have good contacts get ahead. & Está bien que quienes tienen buenos contactos salgan adelante.\\
\bottomrule
\end{tabu}}
\end{table}

\pagebreak

@@

With the objective of evaluating the effect of the indicators ordering,
the respondents (\emph{n = 2141}) were randomly divided into three
different order versions as explained in \textbf{Figure 1}. The scale
was presented to the first group (\emph{n = 712}) in the order that
appears in Table 2. For the second group (\emph{n = 717}), the order of
the items was organized according to the topics of the items, e.g.~for
the topic of hard work the item about perception was followed by the
item about preference, and te same for the rest of the topics. Finally,
for the third group (\emph{n = 712}) the items were completely
randomized.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{../input/images/app_mod.png}
\caption{Survey flow}
\end{figure}

@@

@@

@@

@@

\leavevmode\hypertarget{ref-duru-bellat_whos_2012}{}%
Duru-Bellat, Marie, and Elise Tenret. 2012. ``Who's for Meritocracy?
Individual and Contextual Variations in the Faith.'' \emph{Comparative
Education Review} 56 (2): 223--47. \url{https://doi.org/10.1086/661290}.

@@

@@

\leavevmode\hypertarget{ref-mijs_paradox_2019}{}%
Mijs, Jonathan J B. 2019. ``The Paradox of Inequality: Income Inequality
and Belief in Meritocracy Go Hand in Hand.'' \emph{Socio-Economic
Review}, January. \url{https://doi.org/10.1093/ser/mwy051}.

@@

\leavevmode\hypertarget{ref-reynolds_perceptions_2014}{}%
Reynolds, Jeremy, and He Xian. 2014. ``Perceptions of Meritocracy in the
Land of Opportunity.'' \emph{Research in Social Stratification and
Mobility} 36 (June): 121--37.
\url{https://doi.org/10.1016/j.rssm.2014.03.001}.

@@
